Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-21 head.tex
ready for merge

\author[add1]{Shengkai Chen}
\author[add2,add1]{Shuiliang Fang\corref{cor1}}
\author[add2]{Tao Peng}
\author[add2]{Renzhong Tang}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\begin{abstract}
With cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
Ecosystem of cloud manufacturing has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information, which will help optimize for the overall industry. In this paper, an original operation mode with three extensions are proposed to describe the life cycle vicissitude of each resource. We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.

>>>>

\author[add1]{Shengkai Chen}
\author[add2,add1]{Shuiliang Fang\corref{cor1}}
\author[add1]{Tao Peng}
\author[add1]{Renzhong Tang}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\begin{abstract}
With cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
Ecosystem of cloud manufacturing has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information, which will help optimize for the overall industry. In this paper, an original operation mode with three extensions are proposed to describe the life cycle vicissitude of each resource. We designed an agent-based model to simulate the ecosystem from the very beginning, and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.
